{mscstexta4r}

### 2016-06-15 README.Rmd
Documentation update

Per Microsoft's website, the [Text Analytics REST API](https://www.microsoft.com/cognitive-services/en-us/text-analytics/documentation)
is a suite of text analytics web services built with Azure Machine Learning that
can be used to analyze unstructured text. The API supports four text analysis
operations:

@@

If you're calling `textaDetectTopics()` in synchronous mode within the R console
REPL (interactive mode), it will **appear as if the console has hanged**. This
is *EXPECTED*. The function hasn't crashed. It is simply in "sleep mode",
activating itself periodically and then going back to sleep, until the results
have become available. In sleep mode, even though it appears "stuck",
`textaDetectTopics()` doesn't use any CPU resources. While the function is
operating in sleep mode, you *WILL NOT* be able to use the console before the
function completes. If you need to operate the console while topic detection is
being performed by the Microsoft Cognitive services servers, you should call
`textaDetectTopics()` in asynchronous mode and then call
`textaDetectTopicsStatus()` yourself repeatedly afterwards, until results are
available.

@@

@@

This package is certainly functional. It's also the first time it is available
on CRAN. Therefore, if you observe unexpected behaviors (a.k.a. bugs), please be
kind enough to submit a bug report on GitHub (not via email) with a minimal
reproducible example [here](https://github.com/philferriere/mscstexta4r/issues).

>>>>

Per Microsoft's website, the [Text Analytics REST API](https://www.microsoft.com/cognitive-services/en-us/text-analytics/documentation)
is a suite of text analytics web services built with Azure Machine Learning that
can be used to analyze unstructured text. The API supports the following text
analysis operations:

@@

If you're calling `textaDetectTopics()` in synchronous mode within the R console
REPL (interactive mode), it will **appear as if the console has hanged**. This
is *EXPECTED*. The function hasn't crashed. It is simply in "sleep mode",
activating itself periodically and then going back to sleep, until the results
have become available. In sleep mode, even though it appears "stuck",
`textaDetectTopics()` doesn't use any CPU resources. While the function is
operating in sleep mode, you *WILL NOT* be able to use the console before the
function completes.

If you need to operate the console while topic detection is being performed by
the Microsoft Cognitive services servers, you should call `textaDetectTopics()`
in asynchronous mode and then call `textaDetectTopicsStatus()` yourself
repeatedly afterwards, until results are available.

@@

## Related Microsoft Cognitive Services Packages

`{mscsweblm4r}`, a R Client for the Microsoft Cognitive Services **Web Language
Model** REST API, is also available on [CRAN](https://cran.r-project.org/package=mscsweblm4r)

@@

Please report any issues or bugs [here](https://github.com/philferriere/mscstexta4r/issues).
